---
title: "Script for populistAttitudes_2018.csv"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("gdata")
#install.packages("dplyr")
#install.packages("car")
#install.packages("psych")
#install.packages("Hmisc")
#install.packages("GPArotation")
#install.packages("QuantPsyc")
#install.packages("Rcmdr")
#install.packages("apaTables")
#install.packages("MBESS")

library(MBESS)
library(apaTables)
library(dplyr)
library(Rcmdr)
library(gdata)
library(car)
library(psych)
library(Hmisc)
library(QuantPsyc)
library(DescTools) 

```

## read in data
```{r Daten einlesen}
data <- read.table("dataSet_populistAttitudes_2018.csv", header = TRUE, sep =";", na.strings ="-9")
```

## Exclusion criteria
### Consten 
We will use only the data of participants who gave their consent.
```{r Einverstaendniserklaerung}
data <-data[ data$CO01 == 1, ]
data <-data[ data$CO02 == 1, ]
data <-data[ data$CO03 == 1, ]
data <-data[ data$VW01 == 1, ]
```
### Migration Background
We will only use data of participants with the german citizenship and without migration background.
```{r}
data <-data[ data$SD07 == 1, ]
data <-data[ data$SD08 == 1, ]
```

### Completeness of items regarding populist attitudes
We will only include participants who answered all the questions regarding populist attitudes (PopAtt12).
```{r}
data <-data[ is.na(data$PA04_01) == FALSE, ]
data <-data[ is.na(data$PA04_02) == FALSE, ]
data <-data[ is.na(data$PA04_03) == FALSE, ]
data <-data[ is.na(data$PA04_04) == FALSE, ]
data <-data[ is.na(data$PA04_05) == FALSE, ]
data <-data[ is.na(data$PA04_06) == FALSE, ]
data <-data[ is.na(data$PA04_07) == FALSE, ]
data <-data[ is.na(data$PA04_08) == FALSE, ]
data <-data[ is.na(data$PA04_09) == FALSE, ]
data <-data[ is.na(data$PA04_10) == FALSE, ]
data <-data[ is.na(data$PA04_11) == FALSE, ]
data <-data[ is.na(data$PA04_12) == FALSE, ]
```

### Completeness Media Usage 
We will only include participants who answered all the questions regarding media usage. 
```{r}
data <-data[ is.na(data$MN01_01) == FALSE, ]
data <-data[ is.na(data$MN01_02) == FALSE, ]
data <-data[ is.na(data$MN01_03) == FALSE, ]
data <-data[ is.na(data$MN01_04) == FALSE, ]
data <-data[ is.na(data$MN01_05) == FALSE, ]
```

### at this point: 
xxx questionnaires will be used in the analysis. 

# Data preparation 
### Change variable names for easier handeling 
```{r}
library(gdata)
data <- rename.vars(data, 
                    from=c("ï..CASE"),
                    to=c("CASE"))

```

###  Delete unnecessary variables 
We wil select only the data relevant for our analysis.   
```{r}
data.red <- data
data.red <- data.red[,c(1, 3:5, 16:27,55:59, 79:104)]

```

### Change the type  of the variables appropriately 
(e.g. factors, characters, integers,...)
```{r}
# Change gender to factor
data.red$SD01.f <- factor(data.red$SD01,
                          levels=c(1,2,3),
                          labels=c("maennlich", "weiblich", "sonstiges"))

# Change education to factor
data.red$SD04.f <-factor(data.red$SD04,
                         levels=c(1,2,3,4,5,6,7,8,9),
                         labels=c("noch in der Schule", "Schule beendet ohne Abschluss",
                                  "Volksschulabschluss", "Mittlere Reife", "Lehre",
                                  "Fachabi", "Abi", "Hochschulabschluss",
                                  "anderer Abschluss"))

# Change province to factor 
data.red$SD06.f <-factor(data.red$SD06,
                         levels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17),
                         labels=c("BaWue", "Bayern", "Berlin", "Brandenburg",
                                  "Bremen", "Hamburg", "Hessen", "MeckPom", 
                                  "Niedersachsen", "NRW", "RLP", "Saarland",
                                  "Sachsen", "Sachsen-Anhalt", "Schleswig-Holstein",
                                  "Thueringen", "Ausland"))


```

### Maximum Longstring 
Did a person chose the same answer all the time (e.g. always the 1)? We will check it here, the participant will be excluded if that is the case. 
```{r}
## Create the appropriate function:
maxRun <- function(x) max(rle(x)$lengths)

## Use the function for our dataset 
data.red %>%
  dplyr::select(PA04_01:KV09_05) %>%
  dplyr::mutate(MaxRun = apply( ., 1, FUN=maxRun)) %>%
  dplyr::select(MaxRun) %>%
  data.frame(data.red, .) -> data.red.temp

data.red.temp %>%
  arrange(desc(MaxRun)) %>%
  dplyr::select(PA04_01:KV09_05, MaxRun) %>%
  slice(1:50)

data.red.temp %>% dplyr::select(MaxRun) %>% table

# No, no person has always given the same response. No participant needs to be excluded. 
```

### Participant standard deviation
We calculate a standard deviation for every participant. If a participant shows a very low standard deviation, it is an indication for untrustworthy answers. 
```{r}
data.red %>%
  dplyr::select(PA04_01:KV09_05)  %>%
  dplyr::mutate(SD = apply( ., 1, FUN=sd, na.rm = TRUE)) %>%
  dplyr::select(SD) %>%
  data.frame(data.red.temp, .) -> data.red.temp

data.red.temp %>%
  arrange(desc(SD)) %>%
  dplyr::select(PA04_01:KV09_05, SD) %>%
  slice(1:50)

data.red.temp %>% dplyr::select(SD) %>% round(.,1) %>% table %>% plot
# all participants seem to have an unobstrusive standard deviation. 

```


## Create mean of scales that are to be used. 
```{r}

# Populism (PopAtt12)

data.red$PopAtt <- rowMeans(data.red[c("PA04_01", "PA04_02", "PA04_03", "PA04_04", 
                                       "PA04_05", "PA04_06", "PA04_07", "PA04_08", 
                                       "PA04_09", "PA04_10", "PA04_11", "PA04_12")], 
                            na.rm = TRUE)

# Media scepticism  
data.red$MedSkep <- rowMeans(data.red[c("KV03_01", "KV03_02","KV03_03", "KV03_04", "KV03_05")], na.rm = TRUE)

# National identity
data.red$NatId <- rowMeans(data.red[c("KV04_01", "KV04_02", "KV04_03", "KV04_04")], na.rm = TRUE)

# Political Efficacy  
data.red$Po_Eff_Ges <- rowMeans(data.red[c("KV07_01", "KV07_02", "KV07_03", "KV07_04")], na.rm = TRUE)
```

## Outlier and Winsorizing
We will deal with outliers by using the MAD (Median Absoult Deviation) and Winsorizing. 
```{r}
# Change integers to numerics 
# As numerics, decimals are possible, too. 

## Medienartnutzung 
data.red$MN01_01 <- as.numeric(data.red$MN01_01) # TV
data.red$MN01_02 <- as.numeric(data.red$MN01_02) # Radio
data.red$MN01_03 <- as.numeric(data.red$MN01_03) # Print newspapers
data.red$MN01_04 <- as.numeric(data.red$MN01_04) # Online newspapers
data.red$MN01_05 <- as.numeric(data.red$MN01_05) # social media 

## Populismus nach Hameleers 
data.red$PopAtt <- as.numeric(data.red$PopAtt) # 

## Control variables  
data.red$KV01_01 <- as.numeric(data.red$KV01_01) # Medienvertrauen
data.red$MedSkep <- as.numeric(data.red$MedSkep) # Medienskeptizismus
data.red$NatId <- as.numeric(data.red$NatId) # nationale Identit?t
data.red$Po_Eff_Ges <- as.numeric(data.red$Po_Eff_Ges) # Political Efficacy
data.red$KV09_01 <- as.numeric(data.red$KV09_01) # Vorurteile gegen?ber Gefl?chteten

## Create an object for the wonsorized data. 
data.win <- data.red

###  Winsorizing

## Media usage  
# TV
High_Bench <- median(data.red$MN01_01) + 3*mad(data.red$MN01_01)
Low_Bench <- median(data.red$MN01_01) - 3*mad(data.red$MN01_01)
data.win$MN01_1 <- Winsorize(data.win$MN01_01,  minval = Low_Bench, maxval = High_Bench)

# Radio 
High_Bench <- median(data.red$MN01_02) + 3*mad(data.red$MN01_02)
Low_Bench <- median(data.red$MN01_02) - 3*mad(data.red$MN01_02)
data.win$MN01_02 <- Winsorize(data.win$MN01_02,  minval = Low_Bench, maxval = High_Bench)

# Print newspaper 
High_Bench <- median(data.red$MN01_03) + 3*mad(data.red$MN01_03)
Low_Bench <- median(data.red$MN01_03) - 3*mad(data.red$MN01_03)
data.win$MN01_03 <- Winsorize(data.win$MN01_03,  minval = Low_Bench, maxval = High_Bench)

# Online newspaper 
High_Bench <- median(data.red$MN01_04) + 3*mad(data.red$MN01_04)
Low_Bench <- median(data.red$MN01_04) - 3*mad(data.red$MN01_04)
data.win$MN01_04 <- Winsorize(data.win$MN01_04,  minval = Low_Bench, maxval = High_Bench)

# Social Medien
High_Bench <- median(data.red$MN01_05) + 3*mad(data.red$MN01_05)
Low_Bench <- median(data.red$MN01_05) - 3*mad(data.red$MN01_05)
data.win$MN01_05 <- Winsorize(data.win$MN01_05,  minval = Low_Bench, maxval = High_Bench)


## Populism
# Populism
High_Bench <- median(data.red$PopAtt) + 3*mad(data.red$PopAtt)
Low_Bench <- median(data.red$PopAtt) - 3*mad(data.red$PopAtt)
data.win$PopAtt <- Winsorize(data.win$PopAtt,  minval = Low_Bench, maxval = High_Bench)

## Control Variables 
# KV01_01
High_Bench <- median(data.red$KV01_01) + 3*mad(data.red$KV01_01)
Low_Bench <- median(data.red$KV01_01) - 3*mad(data.red$KV01_01)
data.win$KV01_01 <- Winsorize(data.win$KV01_01,  minval = Low_Bench, maxval = High_Bench)

# MedSkep
High_Bench <- median(data.red$MedSkep) + 3*mad(data.red$MedSkep)
Low_Bench <- median(data.red$MedSkep) - 3*mad(data.red$MedSkep)
data.win$MedSkep <- Winsorize(data.win$MedSkep,  minval = Low_Bench, maxval = High_Bench)

# NatId
High_Bench <- median(data.red$NatId) + 3*mad(data.red$NatId)
Low_Bench <- median(data.red$NatId) - 3*mad(data.red$NatId)
data.win$NatId <- Winsorize(data.win$NatId,  minval = Low_Bench, maxval = High_Bench)

# Po_Eff_Ges
High_Bench <- median(data.red$Po_Eff_Ges) + 3*mad(data.red$Po_Eff_Ges)
Low_Bench <- median(data.red$Po_Eff_Ges) - 3*mad(data.red$Po_Eff_Ges)
data.win$Po_Eff_Ges <- Winsorize(data.win$Po_Eff_Ges,  minval = Low_Bench, maxval = High_Bench)

# KV09_01
High_Bench <- median(data.red$KV09_01) + 3*mad(data.red$KV09_01)
Low_Bench <- median(data.red$KV09_01) - 3*mad(data.red$KV09_01)
data.win$KV09_01 <- Winsorize(data.win$KV09_01,  minval = Low_Bench, maxval = High_Bench)


#### Important ####
# If you use the following command, you will proceed with the winsorized data. 
# If you do not use the following command, you will use the not-wonsorized data. 

# data.red <- data.win
```

## Item statistics 
We will create a table with all the item statistics per variable. 
```{r}
data.red %>%
  dplyr::select(PA04_01:KV09_05) %>%
  psych::describe() %>%
  dplyr::select(-c(vars,trimmed,mad,range:se)) -> Item_Describe

data.red %>%
  dplyr::select(PA04_01:KV09_05) %>%
    apply(2, shapiro.test) -> Shapiro

sapply(Shapiro, function(x) x[1]) %>% as.numeric -> Sh.Statistik
sapply(Shapiro, function(x) x[2]) %>% as.numeric -> Sh.pWert

data.frame(Item_Describe, Sh.Statistik, Sh.pWert) -> Tabelle  

# In this table, you will find the median, the sd, the mean and a test for 
# normal distribution.
# the responses to the items are not normally distributed.  
```

## Intercorrelationmatrix
We create an intercorrelationmatrix for all variables. 
```{r}
InterCorrel_subset <- data.red[, 5:38]

InterCorrel <- rcorr(as.matrix(InterCorrel_subset))

# We will save the matrix to a csv file. 
write.csv(InterCorrel[[1]], "Interkorrelationsmatrix_R.csv")
write.csv(InterCorrel[[2]], "Interkorrelationsmatrix_NumberOfN.csv")
write.csv(InterCorrel[[3]], "Interkorrelationsmatrix_pValue.csv")
```

## Cronbachs Alpha 
We calculate Cronbachs Alpha for all scales. 
```{r}
# Populism # .91
psych::alpha(data.red[ ,5:16])

# control variables  
## Political Efficacy .68
psych::alpha(data.red[ ,c("KV07_01","KV07_02", "KV07_03", "KV07_04")])

## national identity # .88
psych::alpha(data.red[ ,c("KV04_01", "KV04_02", "KV04_03", "KV04_04")])

## Media skepticism  # .85
psych::alpha(data.red[ ,c("KV03_01", "KV03_02", "KV03_03", "KV03_04", "KV03_05")])


```

### Description of our sample 
```{r}
## Gender
table(data.red$SD01)
# 65 male
# 75 female
# 3 "other"

## Age
mean(data.red$SD02_01)
sd(data.red$SD02_01)


## highest education
table(data.red$SD04.f)
prop.table(table(data.red$SD04.f))*100

## German province of residence 
# absolute frequency
table(data.red$SD06.f)
# relative frequency  
prop.table(table(data.red$SD06.f))*100

```

### Exploratory Factor Analysis 
#### EFA Populism
Exploratory Factor Analysis for the 12 Populism Items (PopAtt12)
```{r}

# 1. Create a subset of the populist items 
EFA_1 <- data.red[,5:16]

# 2. We will only take into consideration those participants who answerd all relevant items. 
EFA_1 <- na.omit(EFA_1)

# 3.) Calculate the correlation matrix
# Warning: EFA_1 is a data frame , rcorr() need a matrix.
# Convert data frame to matrix and calculate the correlation matrix. 
rcorr(as.matrix(EFA_1))

# Create the matrix 
Matrix_EFA_1 <- as.matrix(EFA_1)

# 4.) Calculate the Kaiser-Mayer-Olkin (KMO) criterium. 
KMO(Matrix_EFA_1)
# The total KMO = .91; that is a good value. 
# All individual values are above .6, thats good. 

# 5.) Do the Barteltt's test of sphericity
cortest.bartlett(Matrix_EFA_1)
# The test is significant
# We can assume that it is not an indentity matrix. 

# 6.) Identify the facotrs
# "fa" for principle axis factoring
EFAparallel1 <- fa.parallel(EFA_1, fa="fa")

# Print eigenvalues. 
EFAparallel1$fa.values

# Print simulated eigenvalues.
EFAparallel1$fa.sim

## Stop criterium: Parallel analysis of Horn recommends 2 factors

# 7.) Fixed number of factors and rotation with 2 factors 
# oblique rotation
EFAoblique_1 <- fa(EFA_1, 2, fm="pa", rotate="promax")
print(EFAoblique_1, digits =2, cut =.3, sort = TRUE)
EFAoblique_1
## The factor analysis pointed to 2 factors

## Cronbachs alpha for two factors: 
## Factor 1
psych::alpha(na.omit(EFA_1[ ,c("PA04_01", "PA04_02", "PA04_03", "PA04_04", "PA04_05",
                       "PA04_06", "PA04_07", "PA04_08")]))
## Factor 2
psych::alpha(na.omit(EFA_1[ ,c("PA04_09","PA04_10", "PA04_11", "PA04_12")]))

```


# Interference statistic
### Correlation
Check requirements:
- Linearity of the relation
- Normal distribution of X and Y

### Linear Regression
Check requirements:
- Linearity of the relation based on scatterplots

### Multiple Regression
Check requirements: 
- Multicolinearity
- Is the model specified correctly (is the relationsship linear)?
- Are the residuals normally distributed?
- Homoscedacity?
- Are there outliers? 


## H1: Populism and Social Media 
People with populist attitudes use more social media.
```{r}
### Calculation without control variables 

# Scatterplot to check linearity 
plot(data.red$MN01_05, data.red$PopAtt, main ="lowess(Pop)")
lines(lowess(data.red$MN01_05 ~ data.red$PopAtt), col=2)
abline(lm(data.red$MN01_05 ~ data.red$PopAtt))

# Specify regression model
mod_med_SM <- lm(scale(MN01_05) ~ scale(PopAtt) , data=data.red, na.action = na.exclude)
summary(mod_med_SM)

# calculate beta-coefficient 
lm.beta(mod_med_SM)

# create table 
apa.reg.table(mod_med_SM, filename = "H1_ohneKV.doc", table.number = 1,
prop.var.conf.level = 0.95)
```

H1 with control variables 
```{r}

# 1.) step 1: create subset with all the important variables 
Subset <- data.red[c("PopAtt", "MN01_05", "KV01_01", "MedSkep", "NatId", "Po_Eff_Ges", "KV09_01")] 

# 2.) include only complete data sets
Subset.c<- na.omit(Subset)

## it was not possible to create normal distribution through transformation. 

# 3.) Scale the data
Subset.c$MN01_05.cen <- scale(Subset.c$MN01_05, scale=FALSE)
Subset.c$PopAtt.cen <- scale(Subset.c$PopAtt, scale=FALSE)
Subset.c$KV01_01.cen <- scale(Subset.c$KV01_01, scale=FALSE)
Subset.c$MedSkep.cen <- scale(Subset.c$MedSkep, scale=FALSE)
Subset.c$NatId.cen <- scale(Subset.c$NatId, scale=FALSE)
Subset.c$Po_Eff_Ges.cen <- scale(Subset.c$Po_Eff_Ges, scale=FALSE)
Subset.c$KV09_01.cen <- scale(Subset.c$KV09_01, scale=FALSE)


# 4.) Specify data
Modell <-lm(MN01_05.cen ~ MedSkep.cen + NatId.cen + Po_Eff_Ges.cen + KV09_01.cen 
            + PopAtt.cen + KV01_01.cen , data=Subset.c)

summary(Modell)

# 5.) check multicolinearity 
library(car)
vif(Modell)
1/vif(Modell)
# Multikollinearit?t okay, wenn VID < 10 
# Multikollinearit?t okay, wenn TOL > .1

# 6.) Check requirements with plot.
plot(Modell)

# Deviation from normal distribution
# therefore: use bootstrapping for the coefficients 

# 7.) Create model with control variables. 
Modell_1 <- lm(MN01_05.cen ~ PopAtt.cen, data=Subset.c) 
Modell_2 <- lm(MN01_05.cen ~  KV01_01.cen + MedSkep.cen + NatId.cen + 
                 Po_Eff_Ges.cen + KV09_01.cen , data=Subset.c)
Modell_3 <-lm(MN01_05.cen ~ KV01_01.cen + MedSkep.cen + NatId.cen + 
                Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen, data=Subset.c)

summary(Modell_1)
summary(Modell_2)
summary(Modell_3)

# Calculate increment in R and F-deviation
summary(Modell_3)$r.squared - summary(Modell_2)$r.squared
anova(Modell_2, Modell_3)

# Calculate beta-Koefficients for model 
lm.beta(Modell_2)
lm.beta(Modell_3)

# create output table:
apa.reg.table(Modell_1, filename = "H1_Step1__Pr?d_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_2, filename = "H1_Step1_KV_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_3, filename = "H1_Step2_results.doc", table.number = 1,
prop.var.conf.level = 0.95)

#### results ####
# if you control for variables, the p-value is = .055
# it is just not significant anymore
```

### H1b Populism and TV - usage
```{r}
### without control variables 

# Scatterplot TV
plot(data.red$MN01_01, data.red$PopAtt, main ="lowess(Pop)")
lines(lowess(data.red$MN01_01 ~ data.red$PopAtt), col=2)
abline(lm(data.red$MN01_01 ~ data.red$PopAtt))

# Regression
Modell <- lm(scale(MN01_01) ~ scale(PopAtt) , data=data.red, na.action = na.exclude)
summary(Modell)
lm.beta(Modell)

# Create table
apa.reg.table(Modell, filename = "H1_TV_oKV.doc", table.number = 1,
prop.var.conf.level = 0.95)

## significatn correlation! 
```

H1b with control variables 
```{r}

### With control variables 
options(scipen=999)
#1. Step 1: Create a subset 
Subset <- data.red[c("PopAtt", "MN01_01", "KV01_01", "MedSkep", "NatId", "Po_Eff_Ges", "KV09_01")] 

# 2.) Delete people who have missing values 
Subset.c<- na.omit(Subset)

## it was not possible to create normal distribution through transformation. 

# 3.) Scale
Subset.c$MN01_01.cen <- scale(Subset.c$MN01_01, scale=FALSE)
Subset.c$PopAtt.cen <- scale(Subset.c$PopAtt, scale=FALSE)
Subset.c$KV01_01.cen <- scale(Subset.c$KV01_01, scale=FALSE)
Subset.c$MedSkep.cen <- scale(Subset.c$MedSkep, scale=FALSE)
Subset.c$NatId.cen <- scale(Subset.c$NatId, scale=FALSE)
Subset.c$Po_Eff_Ges.cen <- scale(Subset.c$Po_Eff_Ges, scale=FALSE)
Subset.c$KV09_01.cen <- scale(Subset.c$KV09_01, scale=FALSE)


# 4.) Specify model 
Modell <-lm(MN01_01.cen ~ MedSkep.cen + NatId.cen + Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen + KV01_01.cen , data=Subset.c)
summary(Modell)

# 5.) Multicolinearity 
library(car)
vif(Modell)
1/vif(Modell)
# multiconlineraity ok if  VID < 10 
# Multicolinearity ok if TOL > .1

# 6.) Plot
plot(Modell)

## The plots do not look good
# Deviation from normal distribution 
# Therefore: Bootstrapping 

# 7.) Normal calculation of the increment of R  

summary(Modell)

# 8.) Control Variables 
Modell_1 <- lm(MN01_01.cen ~ PopAtt.cen, data=Subset.c) 
Modell_2 <- lm(MN01_01.cen ~  KV01_01.cen + MedSkep.cen + NatId.cen + 
                 Po_Eff_Ges.cen + KV09_01.cen , data=Subset.c)
Modell_3 <-lm(MN01_01.cen ~ KV01_01.cen + MedSkep.cen + NatId.cen + 
                Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen, data=Subset.c)

summary(Modell_1)
summary(Modell_2)
summary(Modell_3)


summary(Modell_3)$r.squared - summary(Modell_2)$r.squared
anova(Modell_2, Modell_3)

lm.beta(Modell_2)
lm.beta(Modell_3)
## H1b with control variables: The patterns is the same, still significant 

# Create output tables 
apa.reg.table(Modell_1, filename = "H1b_Step1__Pred_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_2, filename = "H1b_Step1_KV_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_3, filename = "H1b_Step2_results.doc", table.number = 1,
prop.var.conf.level = 0.95)

## significant correlation with and without controlling for variables 
```
### bis hier hin ###
### H1c Populismus und Radio-Nutzung
```{r}
### Without control variables 

# Improvement of linearity: Square root transformation
data.red$MN01_02.t <- sqrt(data.red$MN01_02)

# Scatterplot Radio
plot(data.red$MN01_02.t, data.red$PopAtt, main ="lowess(Pop)")
lines(lowess(data.red$MN01_02.t ~ data.red$PopAtt), col=2)
abline(lm(data.red$MN01_02.t ~ data.red$PopAtt))

options(scipen=999)
# Regression
Modell <- lm(scale(MN01_02.t) ~ scale(PopAtt) , data=data.red, na.action = na.exclude)
summary(Modell)
lm.beta(Modell)

# Create table with output 
apa.reg.table(Modell, filename = "H1_Radio_oKV.doc", table.number = 1,
prop.var.conf.level = 0.95)

## not significant, linearity is restricted 

```

H1c Populist Attitudes ~ Radio while controling for variables 
```{r}
### With control variables 
options(scipen=999)

# 1.) Step: Create subset 
Subset <- data.red[c("PopAtt", "MN01_02.t", "KV01_01", "MedSkep", "NatId", "Po_Eff_Ges", "KV09_01")] 

# 2.) Delete people who have missing values 
Subset.c<- na.omit(Subset)

## it was not possible to create normal distribution through transformation. 

# 3.) Scale
Subset.c$MN01_02.t.cen <- scale(Subset.c$MN01_02.t, scale=FALSE)
Subset.c$PopAtt.cen <- scale(Subset.c$PopAtt, scale=FALSE)
Subset.c$KV01_01.cen <- scale(Subset.c$KV01_01, scale=FALSE)
Subset.c$MedSkep.cen <- scale(Subset.c$MedSkep, scale=FALSE)
Subset.c$NatId.cen <- scale(Subset.c$NatId, scale=FALSE)
Subset.c$Po_Eff_Ges.cen <- scale(Subset.c$Po_Eff_Ges, scale=FALSE)
Subset.c$KV09_01.cen <- scale(Subset.c$KV09_01, scale=FALSE)


# 4.) Specify Model
Modell <-lm(MN01_02.t.cen ~ MedSkep.cen + NatId.cen + Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen + KV01_01.cen , data=Subset.c)
summary(Modell)

# 5.) Multicolinearity 
library(car)
vif(Modell)
1/vif(Modell)
# Multicolinearity okay, if VID < 10 
# Multicolinearity okay, if TOL > .1

# 6.) Plot
plot(Modell)

# Plot shows no normal distribution
# therefore: Bootstrapping or transformation of the data 

# 7.) Normal calculation of increment in R

summary(Modell)

# 8.) Control variables 
Modell_1 <- lm(MN01_02.t.cen ~ PopAtt.cen, data=Subset.c) 
Modell_2 <- lm(MN01_02.t.cen ~  KV01_01.cen + MedSkep.cen + NatId.cen + 
                 Po_Eff_Ges.cen + KV09_01.cen , data=Subset.c)
Modell_3 <-lm(MN01_02.t.cen ~ KV01_01.cen + MedSkep.cen + NatId.cen + 
                Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen, data=Subset.c)

summary(Modell_1)
summary(Modell_2)
summary(Modell_3)


summary(Modell_3)$r.squared - summary(Modell_2)$r.squared
anova(Modell_2, Modell_3)

lm.beta(Modell_2)
lm.beta(Modell_3)
## H1 with control variables: Pattern stays the same

# Create table with output:
apa.reg.table(Modell_1, filename = "H1c_Step1__Pred_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_2, filename = "H1c_Step1_KV_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_3, filename = "H1c_Step2_results.doc", table.number = 1,
prop.var.conf.level = 0.95)

## With and without control variables not significant 
## With and without Wonsorizing not significant 
```

### H1d Populism and online newspapers 
```{r}
### Without control variables 
data.red$MN01_04.t<- sqrt(data.red$MN01_04)

# Scatterplot online-newspapers
plot(data.red$MN01_04.t, data.red$PopAtt, main ="lowess(Pop)")
lines(lowess(data.red$MN01_04.t ~ data.red$PopAtt), col=2)
abline(lm(data.red$MN01_04.t ~ data.red$PopAtt))

options(scipen=999)
# Regression
Modell <- lm(scale(MN01_04.t) ~ scale(PopAtt) , data=data.red, na.action = na.exclude)
summary(Modell)
lm.beta(Modell)

# Table 
apa.reg.table(Modell, filename = "H1d_OZ_oKV.doc", table.number = 1,
prop.var.conf.level = 0.95)

## not significant
## With and without winsorizing not significant  
```

H1d while controling for variables 
```{r}
### With control variables 
options(scipen=999)

#1.  Step: Create subset 
Subset <- data.red[c("PopAtt", "MN01_04.t", "KV01_01", "MedSkep", "NatId", "Po_Eff_Ges", "KV09_01")] 

# 2.) Delete people who have missing values 
Subset.c<- na.omit(Subset)

## it was not possible to create normal distribution through transformation. 

# 3.) Scale 
Subset.c$MN01_04.t.cen <- scale(Subset.c$MN01_04.t, scale=FALSE)
Subset.c$PopAtt.cen <- scale(Subset.c$PopAtt, scale=FALSE)
Subset.c$KV01_01.cen <- scale(Subset.c$KV01_01, scale=FALSE)
Subset.c$MedSkep.cen <- scale(Subset.c$MedSkep, scale=FALSE)
Subset.c$NatId.cen <- scale(Subset.c$NatId, scale=FALSE)
Subset.c$Po_Eff_Ges.cen <- scale(Subset.c$Po_Eff_Ges, scale=FALSE)
Subset.c$KV09_01.cen <- scale(Subset.c$KV09_01, scale=FALSE)


# 4.) Specify Model
Modell <-lm(MN01_04.t.cen ~ MedSkep.cen + NatId.cen + Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen + KV01_01.cen , data=Subset.c)
summary(Modell)

# 5.) Multicolinearity
library(car)
vif(Modell)
1/vif(Modell)
# Multicolinearity okay, if VID < 10 
# Multicolinearity okay, if TOL > .1

# 6.) Plot
plot(Modell)


# no normal distribution
# therefore: Bootstrapping or transformation of data

# 7.) Normal calculation of increment in R

summary(Modell)

# 8.) Control Variable 
Modell_1 <- lm(MN01_04.t.cen ~ PopAtt.cen, data=Subset.c) 
Modell_2 <- lm(MN01_04.t.cen ~  KV01_01.cen + MedSkep.cen + NatId.cen + 
                 Po_Eff_Ges.cen + KV09_01.cen , data=Subset.c)
Modell_3 <-lm(MN01_04.t.cen ~ KV01_01.cen + MedSkep.cen + NatId.cen + 
                Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen, data=Subset.c)

summary(Modell_1)
summary(Modell_2)
summary(Modell_3)


summary(Modell_3)$r.squared - summary(Modell_2)$r.squared
anova(Modell_2, Modell_3)

lm.beta(Modell_2)
lm.beta(Modell_3)
## H1d with control variables: Pattern stays the same

# Print output in tables 
apa.reg.table(Modell_1, filename = "H1d_Step1__Pred_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_2, filename = "H1d_Step1_KV_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_3, filename = "H1d_Step2_results.doc", table.number = 1,
prop.var.conf.level = 0.95)

## not significant
## with and without wonsorizing
```


### H1e Populism and print newspapers 
```{r}
# lineraity is restricted, transform data 
data.red$MN01_03.t <- sqrt(data.red$MN01_03)

# Scatterplot
plot(data.red$MN01_03.t, data.red$PopAtt, main ="lowess(Pop)")
lines(lowess(data.red$MN01_03.t ~ data.red$PopAtt), col=2)
abline(lm(data.red$MN01_03.t ~ data.red$PopAtt))

options(scipen=999)
# Regression
Modell <- lm(scale(MN01_03.t) ~ scale(PopAtt) , data=data.red, na.action = na.exclude)
summary(Modell)
lm.beta(Modell)

# Create table with output 
apa.reg.table(Modell, filename = "H1e_Z_oKV.doc", table.number = 1,
prop.var.conf.level = 0.95)

## Significant after transformation
## stays significant when controlling for variables 
```

H1e unter Kontrolle der St?rvariablen  
```{r}
### Control Variables 
options(scipen=999)

#1.  Step: Create subset 
Subset <- data.red[c("PopAtt", "MN01_03.t", "KV01_01", "MedSkep", "NatId", "Po_Eff_Ges", "KV09_01")] 

# 2.) Delete people who have missing values 
Subset.c<- na.omit(Subset)

## it was not possible to create normal distribution through transformation. 

# 3.) Scale
Subset.c$MN01_03.t.cen <- scale(Subset.c$MN01_03.t, scale=FALSE)
Subset.c$PopAtt.cen <- scale(Subset.c$PopAtt, scale=FALSE)
Subset.c$KV01_01.cen <- scale(Subset.c$KV01_01, scale=FALSE)
Subset.c$MedSkep.cen <- scale(Subset.c$MedSkep, scale=FALSE)
Subset.c$NatId.cen <- scale(Subset.c$NatId, scale=FALSE)
Subset.c$Po_Eff_Ges.cen <- scale(Subset.c$Po_Eff_Ges, scale=FALSE)
Subset.c$KV09_01.cen <- scale(Subset.c$KV09_01, scale=FALSE)


# 4.) Specify Model
Modell <-lm(MN01_03.t.cen ~ MedSkep.cen + NatId.cen + Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen + KV01_01.cen , data=Subset.c)
summary(Modell)

# 5.) Multicolinearity
library(car)
vif(Modell)
1/vif(Modell)
# Multicolinearity okay, if VID < 10 
# Multicolinearity okay, if TOL > .1

# 6.) Plot
plot(Modell)

## no normal distribution
# Therefore: Bootstrapping or transformaion

# 7.) normal calculation of the increment in R 

summary(Modell)

# 8.) Control Variables 
Modell_1 <- lm(MN01_03.t.cen ~ PopAtt.cen, data=Subset.c) 
Modell_2 <- lm(MN01_03.t.cen ~  KV01_01.cen + MedSkep.cen + NatId.cen + 
                 Po_Eff_Ges.cen + KV09_01.cen , data=Subset.c)
Modell_3 <-lm(MN01_03.t.cen ~ KV01_01.cen + MedSkep.cen + NatId.cen + 
                Po_Eff_Ges.cen + KV09_01.cen + PopAtt.cen, data=Subset.c)

summary(Modell_1)
summary(Modell_2)
summary(Modell_3)


summary(Modell_3)$r.squared - summary(Modell_2)$r.squared
anova(Modell_2, Modell_3)

lm.beta(Modell_2)
lm.beta(Modell_3)
## H1e with control variables: PAtters stays the same 

# Print output to table
apa.reg.table(Modell_1, filename = "H1e_Step1__Pred_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_2, filename = "H1e_Step1_KV_results.doc", table.number = 1,
prop.var.conf.level = 0.95)
apa.reg.table(Modell_3, filename = "H1e_Step2_results.doc", table.number = 1,
prop.var.conf.level = 0.95)

## While controling for variables, the relationship between populism and print newspapers stays significant.
```







